Data Flow Analysis\\in the Presence of Correlated Calls

### 2014-12-08 content/background.tex
removing some comments

In this way, the IFDS algorithm reduces the input data-flow problem to a graph-reachability problem.
\begin{example}
  In a taint analysis, $D$ is the set of variables in the program. If a fact $d\in D$ is reachable at a given node, then the variable is considered secret at that node. Otherwise, it is considered not secret. The question ``is $d$ secret at node $n$?'' becomes ``is there a realizable path from (\textsf{start}$_\texttt{main}$,\,\textbf{0}) to $(n,\,d)$?''.
\end{example}
\commentout{\begin{example} 
  In an available-expressions analysis, $D$ is the set of all expressions in the program. If an expression $d\in D$ is reachable at a certain node, it means that it does not need to be recomputed at that node. 
\end{example}}
\begin{example}
  The exploded supergraph for Listing~\ref{list:ccexample} is shown in Figure~\ref{fig:cc_edgefn_example}.
  We can see that there is a realizable path
  from the start node of the exploded graph to the variable \verb's' at~the~node~$\textsf{print(s)}$ in the \verb'B.bar' method. This means that at that node, \verb's' is considered secret.

>>>>

In this way, the IFDS algorithm reduces the input data-flow problem to a graph-reachability problem.
\begin{example}
  In a taint analysis, $D$ is the set of variables in the program. If a fact $d\in D$ is reachable at a given node, then the variable is considered secret at that node. Otherwise, it is considered not secret. The question ``is $d$ secret at node $n$?'' becomes ``is there a realizable path from (\textsf{start}$_\texttt{main}$,\,\textbf{0}) to $(n,\,d)$?''.
\end{example}
\commentout{\begin{example} 
  In an available-expressions analysis, $D$ is the set of all expressions in the program. If an expression $d\in D$ is reachable at a certain node, it means that it does not need to be recomputed at that node. 
\end{example}}
\begin{example}
  The exploded supergraph for Listing~\ref{list:ccexample} is shown in Figure~\ref{fig:cc_edgefn_example}.\mtodo{Tell the reader here to ignore the labels on the edges of the graph?}
  We can see that there is a realizable path
  from the start node of the exploded graph to the variable \verb's' at~the~node~$\textsf{print(s)}$ in the \verb'B.bar' method. This means that at that node, \verb's' is considered secret.

### 2014-12-08 content/impl.tex
removed old comment
removing proof
removing some comments

    \node [n,label=\texttt{s}] (st_b_bar_s) [left=\nd of st_b_bar.west] {};
    \node [n] (print_s) [left=\nd of print.west] {};
    \node [n] (end_b_bar_s) [left=\nd of end_b_bar.west] {};
    \node [n,label=$\Lambda$] (st_b_bar_z) [left=\nd of st_b_bar_s] {};
    \node [n] (print_z) [left=\nd of print_s] {};
    \node [n] (end_b_bar_z) [left=\nd of end_b_bar_s] {};
%B.bar method edges
    \path[->](st_b_bar_z) edge (print_z);
    \path[->](print_z) edge (end_b_bar_z);
    \path[->](st_b_bar_s) edge (print_s);
    \path[->](print_s) edge (end_b_bar_s);
    \path[->,dashed](call_bar_z) edge [out=40,in=140,color=lightsalmonpink] (st_b_bar_z);
    \path[->,dashed](call_bar_v) edge [out=20,in=160,color=lightsalmonpink] node[arrowtext,above right=-.4cm and .4cm,rotate=-10]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt B\}]$} (st_b_bar_s);
    \path[->,dashed](end_b_bar_z) edge [out=210,in=-40,color=lightsalmonpink] (return_bar_z);    
}
\end{tikzpicture}
\caption[An example program demonstrating correlated-call edge functions on the $\Lambda$-node path for Listing~\ref{list:ccexample}]{An example program demonstrating correlated-call edge functions on the $\Lambda$-node path for Listing~\ref{list:ccexample}. All non-labeled edges are implicitly labeled with identity functions $\id$. The variable corresponding to an initial secret value is denoted as $\psi$.}%
  \label{fig:cc_edgefn_example}%
  \end{figure}
\otodo{we agreed to move this figure to the initial example section}
  \mtodo{Move Figure~\ref{fig:cc_edgefn_example} up to where it's mentioned first? If yes, the caption won't make sense.}
  \otodo{Can we combine the IDE Figure\ref{fig:cc_edgefn_example} with the IFDS Figure 4? It should be the same figure, just that Figure\ref{fig:cc_edgefn_example} has labels on the edges. We can initially tell the reader to ignore the labels until later.}

@@

\todo{What does the notation $N^*$ and $N^\#$ mean? What is the difference between the two?}

@@

\begin{lemma}[Precision]\label{lem:subsetifds}
    \otodo{Should we say $\result_{\text{IDE}}$ instead of $\result$ everywhere, to
        be consistent with $\result_{\text{IFDS}}$?}
    For an IFDS problem $P$ and all ${n\in N^*}$,
    \begin{equation}\label{eq:correct}
      \backCC\left(\result(\transCC_R(P))\right)(n)
      \subseteq
      \result_{\text{IFDS}}(P)(n)\,.
    \end{equation}
\end{lemma}
\otodo{We agreed to move the proofs to the appendix.}
\begin{proof}
  The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
  \begin{align*}
    \backCC\left(\result(\transCC_R(P))\right)(n)&=\{(n',\,D_n'^\Subset(\result(\transCC_R(P))))\ |\ n\in N^*\}(n)\\
      &=D_n^\Subset(\result(\transCC_R(P)))\\
      &\subseteq\mvp F(n)\\
      &=\result_\text{IFDS}(P)(n)\,.\qedhere
  \end{align*}
\end{proof}

>>>>

    \node [n,label=\texttt{s}] (st_b_bar_s) [left=\nd of st_b_bar.west] {};
    \node [n] (print_s) [left=\nd of print.west] {};
    \node [n] (end_b_bar_s) [left=\nd of end_b_bar.west] {};
    \node [n,label=$\Lambda$] (st_b_bar_z) [left=\nd of st_b_bar_s] {};
    \node [n] (print_z) [left=\nd of print_s] {};
    \node [n] (end_b_bar_z) [left=\nd of end_b_bar_s] {};
%B.bar method edges
    \path[->](st_b_bar_z) edge (print_z);
    \path[->](print_z) edge (end_b_bar_z);
    \path[->](st_b_bar_s) edge (print_s);
    \path[->](print_s) edge (end_b_bar_s);
    \path[->,dashed](call_bar_z) edge [out=40,in=140,color=lightsalmonpink] (st_b_bar_z);
    \path[->,dashed](call_bar_v) edge [out=20,in=160,color=lightsalmonpink] node[arrowtext,above right=-.4cm and .4cm,rotate=-10]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt B\}]$} (st_b_bar_s);
    \path[->,dashed](end_b_bar_z) edge [out=210,in=-40,color=lightsalmonpink] (return_bar_z);    
}
\end{tikzpicture}
\caption[An example program demonstrating correlated-call edge functions on the $\Lambda$-node path for Listing~\ref{list:ccexample}]{An example program demonstrating correlated-call edge functions on the $\Lambda$-node path for Listing~\ref{list:ccexample}. All non-labeled edges are implicitly labeled with identity functions $\id$. The variable corresponding to an initial secret value is denoted as $\psi$.}%
  \label{fig:cc_edgefn_example}%  
  \end{figure}
\mtodo{In Figure~\ref{fig:cc_edgefn_example}, should we say that $\psi$ corresponds to the function's return value?}
\otodo{we agreed to move this figure to the initial example section}
  \mtodo{Move Figure~\ref{fig:cc_edgefn_example} up to where it's mentioned first? If yes, the caption won't make sense.}

@@

@@

\begin{lemma}[Precision]\label{lem:subsetifds}
    \otodo{Should we say $\result_{\text{IDE}}$ instead of $\result$ everywhere, to
        be consistent with $\result_{\text{IFDS}}$?}
    For an IFDS problem $P$ and all ${n\in N^*}$,
    \begin{equation}\label{eq:correct}
      \backCC\left(\result(\transCC_R(P))\right)(n)
      \subseteq
      \result_{\text{IFDS}}(P)(n)\,.
    \end{equation}
\end{lemma}

### 2014-12-08 content/related.tex
removing some comments

\section{Related Work}
\otodo{should we move Related Work to near the end of the paper?}
IFDS is a version of the functional approach to data-flow analysis developed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}. Their algorithm is based on computing \textit{summary functions} that return the data-flow value at the end of a procedure, given the data-flow value at the start of the procedure. IFDS problems form a more restricted set of data-flow problems: unlike in the functional approach, IFDS flow functions have to be distributive, and the set of data-flow facts $D$ has to be finite. However, the IFDS algorithm is more general than Sharir's and Pnueli's algorithm in that it can handle programs containing local variables and parameters in recursive methods.

>>>>

\section{Related Work}
IFDS is a version of the functional approach to data-flow analysis developed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}. Their algorithm is based on computing \textit{summary functions} that return the data-flow value at the end of a procedure, given the data-flow value at the start of the procedure. IFDS problems form a more restricted set of data-flow problems: unlike in the functional approach, IFDS flow functions have to be distributive, and the set of data-flow facts $D$ has to be finite. However, the IFDS algorithm is more general than Sharir's and Pnueli's algorithm in that it can handle programs containing local variables and parameters in recursive methods.
